---
title: "Between subjects ANOVA"
output:
  html_document:
    df_print: paged
---

```{r}

df <- rbind(
  data.frame(g=1, x=rchisq(30, 1)),
  data.frame(g=2, x=rchisq(30, 2)),
  data.frame(g=3, x=rchisq(30, 5, ncp=3)))

df$g <- factor(df$g)

m1 <- aov(x~g, data=df)
a1 <- anova(m1)
```

There was a significant (not a significant) effect of Group on dependent variable X at the p<.05 level for the
three conditions, F(a,b)=s, p=`r a1[['Pr(>F)']][1]`.

```{r}
t1 <- TukeyHSD(m1, "g")
```

Post hoc comparisons using the Tukey HSD test indicated
that the mean score for Group 1 (_M_ = XX, _SD_ = XX) was significantly different from Group 3 (_M_ = XX, _SD_ = XX).
However, Group 1  (_M_ = XX, _SD_ = XX) did not significantly differ from Group 2.

Visit [ggplot2 documentation](http://ggplot2.org/) and make
a simple plot to illustrate your anova results. TODO

## Retrospective

Why are so many digits printed, way beyond 2 significant digits?

Use kable to format the ANOVA table

What is the difference between the $ list accessor and the [[]] list accessor? (See below)

## More about vectors

```{r}
v <- c(9,10,3)
names(v) <- c("abc","def","xyz")
v
v[c(1,3)]
```

You can also index with a vector of negative numbers. This gets you all elements except those whose indexes are in the index vector (negated):

```{r}
v[-2]
v[c(-1,-length(v))]
```

### Difference Between [ ] and [[ ]]

```{r}
v[2]
v[[2]]
```

The two ways of indexing also exhibit different behavior when used with lists.

```{r}
L <- list (a="xy", b=9, c=TRUE)
L[2] # Notice that the result is still a list
L[[2]] # ... but this is an element of the list
```

A subscript can also be a logical vector, which selects elements in positions where this subscript is TRUE

```{r}
v[c(TRUE,FALSE,TRUE)]
v[v>5]
v[v>5 & v<10]
v[v>9 | v<7]
```

### Stopping R From Dropping Dimensions

```{r}
M <- matrix(1:6,nrow=2,ncol=3)
M
M[,2:ncol(M)]
M[2:nrow(M),]
M[2:nrow(M),,drop=FALSE]
```
