---
title: "t test between two samples"
output:
  html_document:
    df_print: paged
---

Since we didn't collect real data, let us create some normally
distributed data here. You could replace this section with
some code to read in data from an experiment.

```{r}
options(digits=2, scipen=1)

g1 <- rnorm(24, mean=0, sd=.7)
g2 <- rnorm(30, mean=.5, sd=1.2)
```

Now that we have some data,
we can plot it.

```{r}
library(ggplot2)

# ggplot prefers to have all the data in a single data.frame
df <- rbind(data.frame(g=1, x=g1),
            data.frame(g=2, x=g2))

# these are really group labels, not numbers
df$g <- factor(df$g)

ggplot(df) + geom_histogram(aes(x=x, fill=g), binwidth=.1)
```

What does a t-test say?

```{r}
out <- t.test(g1,g2)
```

An independent-samples t-test was conducted to compare
the means of Group 1 and Group 2.
A significant difference in scores were found between
Group 1 (_M_=`r mean(g1)`, _SD_=`r sd(g1)`) and
Group 2 (INSERT CODE), t(`r out$parameter`)=`r out$p.value`.

OR

No significant difference in scores could be found between
Group 1 (_M_=`r mean(g1)`, _SD_=`r sd(g1)`) and
Group 2 (INSERT CODE), t(`r out$parameter`)=`r out$p.value`.

## Retrospective

Fill in the summary statistics for Group 2.

Did you get the same results as your neighbor? Why not?

What other goodies are in the t.test output?

What does the 'factor' function do?

What does the 'rbind' function do?

What happens if we increase the sample size?

Perform a paired t.test on data in sleep.csv

### The for loop

```{r}
for (i in c(10,12,456)) cat ("The square of",i,"is",i^2,"\n")
for (i in 1:5) cat ("The square of",i,"is",i^2,"\n")
```

Experiment: Change the function (i^2) to something else.

### The while loop

```{r}
i <- 2
while (i^20 >= exp(i)) i <- i + 1
i
```

Experiment: Print the expressions i^20 and exp(i)
at every iteration of the while loop.
